\documentclass[11pt]{article}
%Gummi|065|=)
\usepackage[utf8x]{inputenc}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage[spanish]{babel}
\usepackage{mathpazo}
\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{babel}
\SetUnicodeOption{mathletters}
\SetUnicodeOption{autogenerated}
\setlength\parindent{0pt}

\usepackage{listings}
\usepackage{xcolor}
\lstset { %
    language=C++,
    backgroundcolor=\color{black!5},
    basicstyle=\footnotesize,
}

\begin{document}
\begin{enumerate}
\item \textit{Define a higher-order function (or a function object) \texttt{memoize} in your favorite language. This function takes a pure function \texttt{f} as an argument and returns a function that behaves almost exactly like \texttt{f}, except that it only calls the orginal function once for every argument, stores the result internally, and subsequently returns this stored result every time it's called with the same argument.}

\begin{lstlisting}
template<class A, class B>
std::function<B(A)> memoize(std::function<B(A)> f) {
	return [&](A a) {
		static std::map<A,B> memory;
		auto m = memory.find(a);
		if(m != memory.end()) {
			return m->second;
		} else {
			auto b = f(a);
			memory.emplace(a,b);
			return b;
		}
	};
};
\end{lstlisting}

\item \textit{Try to memoize a function from your standard library that you normally use to produce random numbers. Does it work?}

La funci贸n memoizada devuelve durante la duraci贸n del programa el mismo valor.

\item \textit{Most random number generators can be initialized with a seed. Implement a function that takes a seed, calls the random number generator with that seed, and returns the result. memoize that function. Does it work?}

La versi贸n memoizada devuelve al mismo resultado que la versi贸n normal tras repetidas llamadas.

\item \textit{Which of these C++ functions are pure? Try to memoize them and observe what happens when you call them multiple times: memoized and not.}

\item \textit{How many different functions are there from \texttt{Bool} to \texttt{Bool}? Can you implement them all?}
Hay 4:
\begin{lstlisting}
bool f1(bool) { return false; }
bool f2(bool) { return true; }
bool f3(bool b) { return b; }
bool f4(bool b) { return !b; }
\end{lstlisting}

\item \textit{Draw a picture of a category whose only objects are the types \texttt{Void}, \texttt{()} (unit), and \texttt{Bool}; with arrows corresponding to all posible functions between these types. Label the arrows with the names of the functions.}

\begin{tikzcd}
\texttt{Bool} \arrow[loop,"f1/f2/f3/f4" above]
\arrow[r,"()"]
& \texttt{()} \arrow[loop,"id" above] 
& \texttt{Void} \arrow[loop,"absurd" above] \arrow[l,"absurd"] \arrow[ll,bend left,"absurd"]
\end{tikzcd}
\end{enumerate}
\end{document}
