\documentclass[11pt]{article}
%Gummi|065|=)
\usepackage[utf8x]{inputenc}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb}
\usepackage[spanish]{babel}
\usepackage{mathpazo}
\usepackage{verbatim}
\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{babel}
\SetUnicodeOption{mathletters}
\SetUnicodeOption{autogenerated}
\setlength\parindent{0pt}

\usepackage{listings}
\usepackage{xcolor}
\lstset { %
    language=C++,
    backgroundcolor=\color{black!5},
    basicstyle=\footnotesize,
}

\usepackage{amsmath}
\begin{document}
\begin{enumerate}
\item \textit{Express the co-Yoneda embedding in Haskell.}

Como en el texto, vemos que hay una biyección entre las funciones del tipo \texttt{forall x. (x -> a) -> (x -> b)} y del tipo \texttt{a -> b}.
\begin{verbatim}
fromX :: (x -> a) -> x -> b
fromX f x = atob (f x)

atob :: a -> b
atob = fromX id
\end{verbatim}
Dado \texttt{fromX} ó \texttt{atob}, obtenemos la otra función.

\item \textit{Show that the bijection we established between \texttt{fromY} and \texttt{btoa} is an isomorphism (the two mappings are the inverse of each other).}

\item \textit{Work out the Yoneda embedding for a monoid. What functor corresponds to the monoid's single object? What natural transformations correspond to monoid morphisms?}

\item \textit{What is the application of the covariant Yoneda embedding to preorders? (Question suggested by Gershom Bazerman.)}

\item \textit{Yoneda embedding can be used to embed an arbitrary functor category $[C,D]$ in the functor category $[[C,D],Set]$. Figure out how it works on morphisms (which in this case are natural transformations).}
\end{enumerate}
\end{document}
